---
title: "Test Functions"
tutorial:
  id: "Test_01"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: false
    allow_skip: true
    css: ["css/nu-theme.css"]
    
runtime: shiny_prerendered
description: >
  Learn the basics of Quarto.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(ISDSfunctions)
library(gradethis)

gradethis_setup()

isds_setup(isds_exam = FALSE, max_attempt = Inf, retry_cooldown = 0)

knitr::opts_chunk$set(echo = FALSE)

```


```{r, context = "server"}
grade_server("grade")
```

<!-- ```{r, context = "server"} -->

<!-- lock_server("lock0", graded = c("Q-2", "E-3"), graded_pts = c(2, 3)) -->
<!-- reset_server("reset") -->
<!-- ``` -->

```{r}
grade_button_ui(id = "grade")
grade_print_ui(id = "grade")
# grade_output_ui(id = "grade")
# 
# lock_button_ui(id = "lock0")
# reset_button_ui(id = "reset")
```

```{r, Name}
question_blank("Name: ___",
              answer_fn(function(value){
                              if(length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
              correct = "Submitted",
              incorrect = "Submitted",
              allow_retry = FALSE )
```

## Exercises

**Exercise 1:**

A code chunk can be used as a calculator. Try typing 2+2 into the code chunk and running the code.

```{r Ex1a, context = NULL, exercise = TRUE}

```



```{r Ex1a-solution, exercise.reveal_solution = FALSE}
2 + 2
```

```{r Ex1a-code-check}
grade_this_code(
  correct = "Submitted",
  incorrect = "Submitted"
)
```

## Exam


```{r E}

exam( shuffle = FALSE,
  # question("Q1) What's the city miles per gallon for the first observation in the mpg dataframe?",
  #          answer("29"),
  #          answer("18", correct = TRUE),
  #          answer("21"),
  #          allow_retry = TRUE,
  #          try_again = "Submitted",
  #          random_answer_order = TRUE,
  #          options = list(exam = TRUE)),
  question("Q2) What's the city miles per gallon for the first observation in the mpg dataframe?",
           answer("29"),
           answer("18", correct = TRUE),
           answer("21"),
           allow_retry = TRUE,
           try_again = "Submitted",
           random_answer_order = TRUE),
  ISDSfunctions::question_dropdown("Q3) What's the city miles per gallon for the first observation in the mpg dataframe?",
           answer("29"),
           answer("18", correct = TRUE),
           answer("21"),
           allow_retry = TRUE,
           incorrect = "Submitted",
           try_again = "Submitted",
           random_answer_order = TRUE),
  ISDSfunctions::question_wordbank("Q4) What's the city miles per gallon for the first observation in the mpg dataframe?",
           choices = c("a", "b", "c"),
           answer(c("1", "2", "3"), correct = TRUE),
           allow_retry = TRUE,
           incorrect = "Submitted",
           try_again = "Submitted",
           random_answer_order = TRUE)

)
```

## Quiz
```{r Q}

quiz(
  question("Ex4Q2) What's the city miles per gallon for the first observation in the mpg dataframe?",
           answer("29"),
           answer("18", correct = TRUE),
           answer("21"),
           allow_retry = TRUE,
           try_again = "Submitted",
           random_answer_order = TRUE,
           options = list(exam = TRUE)),
  
  ISDSfunctions::question_dropdown("Ex4Q2) What's the city miles per gallon for the first observation in the mpg dataframe?",
           answer("29"),
           answer("18", correct = TRUE),
           answer("21"),
           allow_retry = TRUE,
           incorrect = "Submitted",
           try_again = "Submitted",
           random_answer_order = TRUE),
  question("Q1) Which of the following help ensure research is reproducible? Select all that apply.",
           answer("Copying and pasting results into a word processor"),
           answer("Using a workflow tool such as RMarkdown", correct = TRUE),
           answer("Literate programming (i.e. code that is readable)", correct = TRUE),
           answer("Well-documented data cleaning and analyses", correct = TRUE),
           allow_retry = TRUE,
           random_answer_order = TRUE
           )
  
)
```

## Ex2

**Exercise 2:**

You can **store** output/results into a variable. Storing output allows you to access the variable later on. When working in Posit, these variables will appear in your **Environment** tab.

Fill in the blanks to store the result of `20*40` into the variable `x`. Note that * is the notation for multiply.

```{r Ex2, exercise=TRUE}
x ___ 20*___
```

```{r Ex2-hint-1}
The assignment operator is `<-`
```

```{r Ex2-solution, exercise.reveal_solution = FALSE}
x <- 20*40
```

```{r Ex2-code-check}
grade_this_code()
```


**Exercise 3:**

A **boolean** statement evaluates to TRUE or FALSE. Type any equation that evaluates to `TRUE`.

```{r Ex3, exercise=TRUE}

```

```{r Ex3-solution, exercise.reveal_solution = FALSE}
3 != 2
```

```{r Ex3-check}
grade_this({
  # custom checking code appears here
  if (identical(.result, .solution)) {
    pass("Great work!")
  }
  fail("Try again!")
})
```


**Exercise 4:**

The `mpg` dataset is included in the `ggplot2` package. Print the dataset to answer the following questions. You can "print" output by typing the name of the dataset or variable in a code chunk. Try typing `mpg` in the code chunk and clicking `run`.

```{r Ex4, exercise = TRUE}

```


```{r Ex4-Q}
quiz(caption = NULL,
    # Ex4Q1
  question("Ex4Q1) Which of the following are names of variables in the mpg data frame?",
           answer("audi"),
           answer("manufacturer", correct = TRUE),
           answer("dplyr"),
           answer("year", correct = TRUE),
           answer("drv", correct = TRUE),
           answer("glimpse"),
           answer("chr"),
           allow_retry = TRUE,
           random_answer_order = TRUE), 
  # Ex4Q2
  question("Ex4Q2) What's the city miles per gallon for the first observation in the mpg dataframe?",
           answer("29"),
           answer("18", correct = TRUE),
           answer("21"),
           answer("0"),
           answer("NA"),
           answer("4"), 
           allow_retry = TRUE,
           random_answer_order = TRUE) )
```
