---
title: "Custom question types for learnr tutorials"
tutorial:
  id: "ex_03"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: false
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  This tutorial is for educators to demonstrate how to use word bank, drop down, and fill in the blank questions in learnr tutorials.
---


## Introduction

The `tutorialExtras` package is designed to help customize `learnr` tutorials. It provides functions to... 

1. shuffle questions, randomly select questions, time submissions, prevent feedback until the tutorial is complete, and download an html grade report for submissions
1. grade tutorials, deduct points based on attempt, and download an html output for submissions.
1. create new question types such as `question_wordbank()`, `question_dropdown()`, and `question_blank()`

This tutorial demonstrates how to **create new question types such as `question_wordbank()`, `question_dropdown()`, and `question_blank()`.**


<br>

Thanks to the authors who developed the [learnr](https://github.com/rstudio/learnr/) package, which these functions are derived from. Many thanks to the author of the [sortable](https://github.com/rstudio/sortable) package and a solution thread by "stefan's on Jun 01, 2022" which helped with the code to develop the word bank question type.

## Set up

```{r setup, message = FALSE, warning = FALSE, echo = TRUE}
library(learnr)
library(tidyverse)
library(tutorialExtras)
#library(gradethis)

#gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)

```


## question_blank

To insert a question with one or more blanks into a `learnr` quiz, use `question_blank()`.

You must provide the correct answers, using the `learnr` `answer()` function. The first blank should correspond to the first `answer()` and so forth. If there are multiple correct answers for a blank then this can be defined in an `answer_fn()`.

The user must have all blanks in a question correct in order for the question to be marked correct.

```{r A, echo = TRUE}
quiz(caption = NULL,
    question_blank("The explanatory variable goes on the ___ axis and the response variable goes on the ___ axis",
    answer_fn(function(value){if (value %in% c("x", "X") ) {
                                return(mark_as(TRUE))}
                              return(mark_as(FALSE) )
                              }),
    answer_fn(function(value){if (value %in% c("y", "Y") ) {
                                return(mark_as(TRUE))}
                              return(mark_as(FALSE) )
                              }),
    allow_retry = TRUE
  ),
  question_blank(
     "3 + ___ = 5 <br/>
      ___ - 4 = 4 <br/>
      12 / 2 = ___",
     learnr::answer("2", correct = TRUE),
     learnr::answer("8", correct = TRUE),
     learnr::answer("6", correct = TRUE),
     allow_retry = TRUE
   )
)

```


## question_wordbank

To insert a wordbank question into a `learnr` quiz, use `question_wordbank()`.

`choices` should be a vector of statements to be matched with.

`answer()` should contain a vector that corresponds to the answers for `choices`. The first answer here "median" matches the first `choices` argument "The center of a list of numbers", and so forth. Be sure to set `correct = TRUE`.

```{r B, echo = TRUE}
quiz(caption = NULL,
    question_wordbank("Match the following words with their definitions.",
            choices = c("The center of a list of numbers", 
                        "The sum of a list of numbers, divided by the number of elements in the list.",  
                        "The most common (frequent) value."),
            answer(c("median", "mean", "mode"), correct = TRUE),
            allow_retry = TRUE )
)
```


`wordbank` is an optional parameter that allows you to add more selection options to the wordbank than possible answers. At a minimum the `wordbank` must contain the correct answers. The arguments in the `wordbank` will be displayed randomly by default.

```{r C, echo = TRUE}
quiz(caption = NULL,
    question_wordbank("Match the following words with their definitions.",
            choices = c("The center of a list of numbers", 
                        "The sum of a list of numbers, divided by the number of elements in the list",  
                        "The most common (frequent) value"),
            wordbank = c("mean", "standard deviation", "median", "mode", "IQR", "range"),
            answer(c("median", "mean", "mode"), correct = TRUE), 
            allow_retry = TRUE )
)
```

If you would like the `wordbank` to appear in alphabetical order add the argument `arrange = "ordered"`. This can be useful so the `wordbank` does not accidentally randomly appear in the correct answer order if there are very few choices.

Or if you set `arrange = "none"`, the `wordbank` will remain in the order you define.

```{r D, echo = TRUE}
quiz(caption = NULL,
    question_wordbank("Match the following words with their definitions.",
            choices = c("The center of a list of numbers",
                        "The sum of a list of numbers, divided by the number of elements in the list", 
                        "The most common (frequent) value"),
            wordbank = c("mean", "standard deviation", "median", "mode", "IQR", "range"),
            arrange = "ordered",
            answer(c("median", "mean", "mode"), correct = TRUE), 
            allow_retry = TRUE )
)
```


## question_dropdown

To insert a radio question in a condensed drop down display into a `learnr` quiz, use `question_dropdown()`.

This choice may be preferred over `question_radio` when there are a lot of choices to save space, or if you do not want the user to see all of the possible answer choices after the question is submitted.

```{r E, echo = TRUE}
question_dropdown(
  "Pick the letter B",
  learnr::answer("A"),
  learnr::answer("B", correct = TRUE),
  learnr::answer("C"),
  learnr::answer("D"),
  learnr::answer("E"),
  learnr::answer("F"),
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```

